Paper Figure Generation

### 2022-06-23 R/PaperFigureGeneration.rmd
Intermediate commit

NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
NHF1ExcisionSiteDataDirectory = file.path(NHF1DataDirectory, "excision_site_analysis")
NHF1GeneralReadSequenceDataDirectory = file.path(NHF1DataDirectory, "general_read_sequences")

@@

```{r figure_2}
plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`,
                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")

plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps Mismatch Trinuc Context")

plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps Mismatch Pos Frequencies")
```

@@

```{r figure_3}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)

plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        expansionOffset = 10, showThreePrimeCutSite = TRUE,
                        showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
# 
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
# 
# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
#                         expansionOffset = 10, showThreePrimeCutSite = TRUE,
#                         showFivePrimeCutSite = TRUE, querySequences = c("TGG"), minReadLength = 18)
```

@@

@@

@@

```{r figure_5}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)

plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

@@

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
# 
# plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime,
#                          NHF1CPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(22:30))
# 
# plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime,
#                          arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(24:30))
# 
# plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime,
#                          yeastCPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(22:25))

@@

```{r figure_6}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 12)

plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 13, maxReadLength = 25)

plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 13, maxReadLength = 25)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 12)
# 
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
# 
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 13, maxReadLength = 25)
```

>>>>

NHF1DataDirectory = file.path(deaminationDataDirectory, "NHF1")
NHF1MismatchesByReadDataDirectory = file.path(NHF1DataDirectory, "mismatches_by_read")
NHF1SequenceAndPositionDataDirectory = file.path(NHF1DataDirectory, "sequence_and_position_analysis")
NHF1ExcisionSiteDataDirectory = file.path(NHF1DataDirectory, "excision_site_analysis")
NHF1GeneralReadSequenceDataDirectory = file.path(NHF1DataDirectory, "general_read_sequences")

@@

```{r figure_2A}
plotMismatchTypeFrequencies(NHF1CPDMismatchDataAllReps$`1h`,
                            title = "NHF1 CPD 1h All Reps Mismatch Type Frequencies")
```
```{r figure_2B}
plotTrinucleotideContext(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                         title = "NHF1 CPD 1h All Reps C>T Mismatch Trinuc Context")
```
```{r figure_2C}
plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, includedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Frequencies")
```
```{r figure_2D}
plotMismatchPositionFrequencies(NHF1CPDMismatchDataAllReps$`1h`, omittedTypes = c("C>T"),
                                title = "NHF1 CPD 1h All Reps !C>T Mismatch Pos Frequencies")
```

@@

```{r figure_3A}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllReps)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllReps, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllReps)
```
```{r figure_3B}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllReps, 
#                                title = "NHF1 CPD All Reps 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_3C}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps$`1h`, title = "NHF1 CPD 1h All Reps General Read TGG Freq",
                        showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
                        expansionOffset = 10, minReadLength = 21, maxReadLength = 27)

### All timepoints together ###
# plotSequenceFrequencies(NHF1CPDTGGSeqFreqAllReps, title = "NHF1 CPD All Reps General Read TGG Freq",
#                         showThreePrimeCutSite = TRUE, showFivePrimeCutSite = TRUE, querySequences = c("TGG"),
#                         expansionOffset = 10, minReadLength = 21, maxReadLength = 27)
```

@@

arabidopsisCPDMismatchDataAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisCPDMismatchDataAllRepsFiltered)) {
  arabidopsisCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", timepoint = names(arabidopsisCPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

yeastCPDMismatchDataAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMismatchDataAllRepsFiltered)) {
  yeastCPDMismatchDataAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$simplifiedMismatches, ".tsv",
    cellType = "yeast", lesion = "CPD", timepoint = names(yeastCPDMismatchDataAllRepsFiltered)[i],
    repitition = "all_reps", filtering = "TGG_filtered"
  ))
}

@@

arabidopsisCPDMMFreqZScoresAllRepsFiltered = arabidopsisCPDTimepoints
for (i in seq_along(arabidopsisCPDMMFreqZScoresAllRepsFiltered)) {
  arabidopsisCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "Arabidopsis", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(arabidopsisCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

yeastCPDMMFreqZScoresAllRepsFiltered = yeastCPDTimepoints
for (i in seq_along(yeastCPDMMFreqZScoresAllRepsFiltered)) {
  yeastCPDMMFreqZScoresAllRepsFiltered[[i]] = fread(generateFilePath(
    arabidopsisSequenceAndPositionDataDirectory, dataTypeStrings$mismatchFrequencyZScores, ".tsv",
    cellType = "yeast", lesion = "CPD", repitition = "all_reps", filtering = "TGG_filtered",
    timepoint = names(yeastCPDMMFreqZScoresAllRepsFiltered)[i], includedMismatches = c("C>T")
  ))
}

@@

```{r figure_5A}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered)
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered)
```
```{r figure_5B}
### Just the 1h timepoint ###
plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Arabidopsis CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)
plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered["1h"], includedTypes = c("C>T"),
                                         title = "Yeast CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Freq",
                                         zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
                                         posType = FIVE_PRIME)

### All timepoints together ###
# plotPositionAcrossTimepointAndReadLength(NHF1CPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = NHF1CPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME)
# plotPositionAcrossTimepointAndReadLength(arabidopsisCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = arabidopsisCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME)
# plotPositionAcrossTimepointAndReadLength(yeastCPDMismatchDataAllRepsFiltered, includedTypes = c("C>T"),
#                                          title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Freq",
#                                          zScoreTables = yeastCPDMMFreqZScoresAllRepsFiltered,
#                                          posType = FIVE_PRIME)
```
```{r figure_5C}
### Just the 1h timepoint ###
plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime[Timepoint == "1h"],
                         NHF1CPDGroupedStatsAllRepsFiltered$five_prime[Timepoint == "1h"],
                         POS_DIFF, title = "NHF1 CPD 1h All Reps TGG-Filtered C>T Mismatch Pos Diff",
                         xAxisBreaks = c(22:30))

@@

### All timepoints together ###
# plotGroupedPositionStats(NHF1CPDGroupedStatsAllRepsFiltered$three_prime,
#                          NHF1CPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "NHF1 CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(22:30))
# 
# plotGroupedPositionStats(arabidopsisCPDGroupedStatsAllRepsFiltered$three_prime,
#                          arabidopsisCPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Arabidopsis CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(24:30))
# 
# plotGroupedPositionStats(yeastCPDGroupedStatsAllRepsFiltered$three_prime,
#                          yeastCPDGroupedStatsAllRepsFiltered$five_prime,
#                          POS_DIFF, title = "Yeast CPD All Reps TGG-Filtered C>T Mismatch Pos Diff",
#                          xAxisBreaks = c(22:25))
```

@@

```{r figure_6A}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h All Reps TGG-Filtered 5' Anchored Nuc Freq",
                               secondaryYAxisLabel = "3' Cut Site Distance",
                               posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 1, maxReadLength = 7)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1FivePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD All Reps TGG-Filtered 5' Anchored Nuc Freq",
#                                secondaryYAxisLabel = "3' Cut Site Distance",
#                                posType = FIVE_PRIME, showThreePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 1, maxReadLength = 7)
```
```{r figure_6B}
### Just the 1h timepoint ###
plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered[Timepoint == "1h"], 
                               title = "NHF1 CPD 1h ALL Reps TGG-Filtered 3' Anchored Purine Freq",
                               yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
                               combineNucleotides = c("AG"), combinedNames = c("Purine"),
                               posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
                               expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotNucFreqVsReadLengthBarPlot(NHF1ThreePrimeMismatchCPDNucFreqAllRepsFiltered, 
#                                title = "NHF1 CPD ALL Reps TGG-Filtered 3' Anchored Purine Freq",
#                                yAxisLabel = "Purine Frequency", secondaryYAxisLabel = "5' Cut Site Distance",
#                                combineNucleotides = c("AG"), combinedNames = c("Purine"),
#                                posType = THREE_PRIME, showFivePrimeCutSite = TRUE,
#                                expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```
```{r figure_6C}
### Just the 1h timepoint ###
plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered$`1h`,
                        title = "NHF1 CPD 1h All Reps TGG-Filtered 3' Anchored YR Freq",
                        secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
                        showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
                        expansionOffset = 10, minReadLength = 19, maxReadLength = 25)

### All timepoints together ###
# plotSequenceFrequencies(NHF1ThreePrimeMMAnchoredCPDSeqFreqAllRepsFiltered,
#                         title = "NHF1 CPD All Reps TGG-Filtered 3' Anchored YR Freq",
#                         secondaryYAxisLabel = "5' Cut Site Distance", yAxisLabel = "YR Frequency",
#                         showFivePrimeCutSite = TRUE, querySequences = c("CG","CA","TG","TA"),
#                         expansionOffset = 10, minReadLength = 19, maxReadLength = 25)
```

```{r read_figure_7_data}
# Note: This file was created manually by combining/modifying a couple different files counting tandem mismatches.
NHF1TandemMismatchCountsComparisonAllReps = fread(generateFilePath(
  NHF1MismatchesByReadDataDirectory, dataTypeStrings$tandemMismatchCountsComparison, ".tsv",
  cellType = "NHF1", repitition = "all_reps"
))
```

```{r figure_7B}
NHF1TandemMismatchCountsComparisonAllReps = NHF1TandemMismatchCountsComparisonAllReps[
  Lesion == "CPD", Timepoint = "1h"
]
print(
    ggplot(NHF1TandemMismatchCountsComparisonAllReps, aes(x = Mismatch_Type, y = Tandem_Mismatches_Count)) +
      geom_bar(aes(fill = Search_Method), stat = "identity", position = "dodge") +
      labs(title = "NHF1 CPD All Reps Tandem Mismatch Counts", x = "Mismatch Type", y = "Tandem Mismatch Count") +
      blankBackground + defaultTextScaling
  )
```
